### 2016-11-07 methodsPaper/tex/materialsAndMethods.tex
Edits to Materials & Methods

\begin{equation}
\delta = 1 - \af \approx \frac{\sum R(x_i)}{\sum R(x_i^\prime)}
\end{equation}

@@

For the purposes of this implementation we limited our analyses to
metropolitan regions of the United States. To idenfity urban
populations we used the National Center for Health Statistics 2013
Urban-Rural Classification Scheme for Counties \cite{ingram2014}. We
eliminated counties in the US with the classifcation of
'nonmetropolitan' (noncore or micropolitan). We used this and similar
classification schemes as well as county and state identifiers in
other datsets (NHTS, ATUS, CDC WONDER) to ensure consistency in our
estimates for input parameters.

To test the new implementation of ITHIM's active transportation
component, we used the UW national metro population estimates for
active travel time (walking and cycling) as the baseline. We obtained
active travel time input parameters for alternate scenarios using
states with large sample sizes. From these examples we were able to
approximate low and high active travel scenarios. Finally we applied
these active travel times to the US metro population to perform the
comparative risk assessment agains the baseline US numbers. We then
examined the sensitivity of disease burden estimates to input
parameters including the active travel time and non-travel activity.

We report total change (averted or increased) in diability adjusted
life years (DALYs) as an estimate of dissease burden change with
alternative scenarions. To estimate DALYs we use a methodology adopted
from previous US implementations of ITHIM which scale Global Budern of
Disease Estimates for the US to smaller populations using mortality
rate ratios \cite{maizlish2013}. Age, sex, and casuse specific
mortalities were obtained form the CDC WONDER database for US metro
counties for the years 2010-2014. Cells with less than 10 deaths were
imputed using R's random integer generator.

>>>>

\begin{equation}
\delta = 1 - \af \approx \frac{\sum_{i=1}^n R(x_i)}{\sum_{i=1}^n R(x_i^\prime)}
\end{equation}

@@

\paragraph{Risk Functions}

We assign risk based on dose-response curves for each of the diseases
included in the model.

\begin{equation}
\RR(x) = \mathrm{e}^{-r \tilde{x}}
\end{equation}

where $\tilde{x} = x^k$, $k=\frac{1}{2}$ and $r$ varies by age-sex
class and disease.  For a table of $r$ values see supplementary
material.

\paragraph{Nationwide Health Benefits to Active Transport}

For the purposes of this implementation we limited our analyses to
metropolitan regions of the United States. To idenfity urban
populations we used the National Center for Health Statistics 2013
Urban-Rural Classification Scheme for Counties \cite{ingram2014}. We
eliminated counties in the US with the classifcation of
`nonmetropolitan' (noncore or micropolitan). We used this and similar
classification schemes as well as county and state identifiers in
other datsets (NHTS, ATUS, CDC WONDER) to ensure consistency in our
estimates for input parameters.

To test the new implementation of ITHIM's active transportation
component, we used the UW national metro population estimates for
active travel time (walking and cycling) as the baseline. We obtained
active travel time input parameters for alternate scenarios using
states with large sample sizes. From these examples we were able to
approximate low and high active travel scenarios. Finally we applied
these active travel times to the US metro population to perform the
comparative risk assessment against the baseline US numbers. We then
examined the sensitivity of disease burden estimates to input
parameters including the active travel time and non-travel activity.
